resevol: an R package for spatially explicit models of pesticide resistance

### 2022-08-02 notebook/ms/ms.Rmd
Fix an error in Figure 1 with the matrix algebra

---
title: 'resevol: an R package for spatially explicit models of pesticide resistance
  given evolving pest genomes'
author: |
  | A. Bradley Duthie&#xb9;&#xb2;, et al.
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2]  alexander.duthie@stir.ac.uk, Biological and Environmental Sciences 3A149
  University of Stirling Stirling, FK9 4LA, UK'
output:
  word_document:
    reference_docx: docx_template.docx
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    toc: no
  pdf_document:
    toc: no
  html_document: default
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{RESEVOL, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: resevol.bib
biblio-style: apalike
---

@@

```{r network, echo = FALSE, fig.width = 6, fig.height = 4, fig.cap = "Example network mapping loci (green circles) to traits (red diamonds) through an intermediate set of hidden layers (blue squares) in the `mine_gmatrix` function. Individual genomes in the resevol R package consist of standard random normal values for loci, real values for black arrows linking nodes, and real values for traits. Values shown for loci and arrows are an example for illustration."}
par(mar = c(0.2, 0.2, 0, 0.2));
plot(x = 0, y = 0, type = "n", xlim = c(0, 1000), ylim = c(0, 1000), 
     xaxt = "n", yaxt = "n", bty = "n", xlab = "", ylab = "");
mtext(side = 1, text = "Internal nodes", cex = 1.25, col = "blue", line = -3);
mtext(side = 2, text = "Loci", cex = 1.25, col = "darkgreen", line = -2);
mtext(side = 4, text = "Traits", cex = 1.25, col = "red", line = -2);
Lx  <- rep(x = 100, times = 3);
Ly  <- seq(from = 250, to = 750, length = 3);
H1x <- rep(x = 400, times = 2);
H1y <- seq(from = 250, to = 750, length = 2);
H2x <- rep(x = 600, times = 2);
H2y <- seq(from = 250, to = 750, length = 2);
Tx  <- rep(x = 900, times = 2);
Ty  <- seq(from = 250, to = 750, length = 2);
points(x = Tx, y = Ty, pch = 23, cex = 8, bg = "red", lwd = 2);
sep_L_points <- c(-50, 0, 50);
sep_N_points <- c(-30, 30);
arrows(x0 = H2x + 52, x1 = Tx[1] - 58, y0 = H2y, y1 = Ty[1] + sep_N_points, 
       length = 0.08, lwd = 3);
arrows(x0 = H2x + 52, x1 = Tx[2] - 58, y0 = H2y, y1 = Ty[2] + sep_N_points, 
       length = 0.08, lwd = 3);
arrows(x0 = Lx + 38, x1 = H1x[1] - 58, y0 = Ly, y1 = H1y[1] + sep_L_points, 
       length = 0.08, lwd = 3);
points(x = H2x, y = H2y, pch = 22, cex = 9, bg = "blue", lwd = 2);
arrows(x0 = H1x + 52, x1 = H2x[1] - 58, y0 = H1y, y1 = H2y[1] + sep_N_points, 
       length = 0.08, lwd = 3);
arrows(x0 = H1x + 52, x1 = H2x[2] - 58, y0 = H1y, y1 = H2y[2] + sep_N_points, 
       length = 0.08, lwd = 3);
points(x = H1x, y = H1y, pch = 22, cex = 9, bg = "blue", lwd = 2);
arrows(x0 = Lx + 38, x1 = H1x[2] - 58, y0 = Ly, y1 = H1y[2] + sep_L_points, 
       length = 0.08, lwd = 3);
points(x = Lx, y = Ly, pch = 21, cex = 6, bg = "darkgreen", lwd = 2);
srnm <- c(0.2, -0.1, 0.1);
text(x = Lx, y = Ly, labels = srnm, col = "white", cex = 0.9);
text(x = 200, y = 790, labels = "0.4", srt = 10, cex = 0.8);
text(x = 200, y = 660, labels = "-1.2", srt = -58, cex = 0.8);
text(x = 270, y = 695, labels = "0.2", srt = 46, cex = 0.8);
text(x = 180, y = 480, labels = "0.1", srt = -40, cex = 0.8);
text(x = 160, y = 340, labels = "-0.6", srt = 54, cex = 0.8);
text(x = 220, y = 255, labels = "2.2", srt = -12, cex = 0.8);
text(x = 490, y = 790, labels = "1.3", srt = 10, cex = 0.8);
text(x = 538, y = 410, labels = "-0.5", srt = -76, cex = 0.8);
text(x = 460, y = 390, labels = "-0.1", srt = 72, cex = 0.8);
text(x = 495, y = 260, labels = "0.0", srt = -12, cex = 0.8);
text(x = 720, y = 790, labels = "2.2", srt = 8, cex = 0.8);
text(x = 720, y = 630, labels = "0.9", srt = -58, cex = 0.8);
text(x = 690, y = 400, labels = "1.6", srt = 54, cex = 0.8);
text(x = 740, y = 260, labels = "0.8", srt = -8, cex = 0.8);
Loci  <- matrix(data = c(0.1, -0.1, 0.2), nrow = 1);
Hdn1  <- matrix(data = c(0.4, -1.2, 0.2, 0.1, -0.6, 2.2), nrow = 3, ncol = 2);
Hdn2  <- matrix(data = c(1.3, -0.1, -0.5, 0.0), nrow = 2, ncol = 2);
Hdn3  <- matrix(data = c(2.2, 1.6, 0.9, 0.8), nrow = 2, ncol = 2);
Tvals <- Loci %*% Hdn1 %*% Hdn2 %*% Hdn3;
text(x = Tx, y = Ty, labels = rev(Tvals), cex = 0.8);
```

>>>>

---
title: 'resevol: an R package for spatially explicit models of pesticide resistance
  given evolving pest genomes'
author: |
  | A. Bradley Duthie&#xb9;&#xb2;, et al.
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2]  alexander.duthie@stir.ac.uk, Biological and Environmental Sciences 3A149
  University of Stirling Stirling, FK9 4LA, UK'
output:
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    toc: no
  pdf_document:
    toc: no
  word_document:
    reference_docx: docx_template.docx
  html_document: default
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{RESEVOL, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: resevol.bib
biblio-style: apalike
---

@@

```{r network, echo = FALSE, fig.width = 6, fig.height = 4, fig.cap = "Example network mapping loci (green circles) to traits (red diamonds) through an intermediate set of hidden layers (blue squares) in the `mine_gmatrix` function. Individual genomes in the resevol R package consist of standard random normal values for loci, real values for black arrows linking nodes, and real values for traits. Values shown for loci and arrows are an example for illustration."}
par(mar = c(0.2, 0.2, 0, 0.2));
plot(x = 0, y = 0, type = "n", xlim = c(0, 1000), ylim = c(0, 1000), 
     xaxt = "n", yaxt = "n", bty = "n", xlab = "", ylab = "");
mtext(side = 1, text = "Internal nodes", cex = 1.25, col = "blue", line = -3);
mtext(side = 2, text = "Loci", cex = 1.25, col = "darkgreen", line = -2);
mtext(side = 4, text = "Traits", cex = 1.25, col = "red", line = -2);
Lx  <- rep(x = 100, times = 3);
Ly  <- seq(from = 250, to = 750, length = 3);
H1x <- rep(x = 400, times = 2);
H1y <- seq(from = 250, to = 750, length = 2);
H2x <- rep(x = 600, times = 2);
H2y <- seq(from = 250, to = 750, length = 2);
Tx  <- rep(x = 900, times = 2);
Ty  <- seq(from = 250, to = 750, length = 2);
points(x = Tx, y = Ty, pch = 23, cex = 8, bg = "red", lwd = 2);
sep_L_points <- c(-50, 0, 50);
sep_N_points <- c(-30, 30);
arrows(x0 = H2x + 52, x1 = Tx[1] - 58, y0 = H2y, y1 = Ty[1] + sep_N_points, 
       length = 0.08, lwd = 3);
arrows(x0 = H2x + 52, x1 = Tx[2] - 58, y0 = H2y, y1 = Ty[2] + sep_N_points, 
       length = 0.08, lwd = 3);
arrows(x0 = Lx + 38, x1 = H1x[1] - 58, y0 = Ly, y1 = H1y[1] + sep_L_points, 
       length = 0.08, lwd = 3);
points(x = H2x, y = H2y, pch = 22, cex = 9, bg = "blue", lwd = 2);
arrows(x0 = H1x + 52, x1 = H2x[1] - 58, y0 = H1y, y1 = H2y[1] + sep_N_points, 
       length = 0.08, lwd = 3);
arrows(x0 = H1x + 52, x1 = H2x[2] - 58, y0 = H1y, y1 = H2y[2] + sep_N_points, 
       length = 0.08, lwd = 3);
points(x = H1x, y = H1y, pch = 22, cex = 9, bg = "blue", lwd = 2);
arrows(x0 = Lx + 38, x1 = H1x[2] - 58, y0 = Ly, y1 = H1y[2] + sep_L_points, 
       length = 0.08, lwd = 3);
points(x = Lx, y = Ly, pch = 21, cex = 6, bg = "darkgreen", lwd = 2);
srnm <- c(0.2, -0.1, 0.1);
text(x = Lx, y = Ly, labels = srnm, col = "white", cex = 0.9);
text(x = 200, y = 790, labels = "0.4", srt = 10, cex = 0.8);
text(x = 200, y = 660, labels = "0.1", srt = -58, cex = 0.8);
text(x = 270, y = 695, labels = "-1.2", srt = 46, cex = 0.8);
text(x = 180, y = 480, labels = "-0.6", srt = -40, cex = 0.8);
text(x = 160, y = 340, labels = "0.2", srt = 54, cex = 0.8);
text(x = 220, y = 255, labels = "2.2", srt = -12, cex = 0.8);
text(x = 490, y = 790, labels = "1.3", srt = 10, cex = 0.8);
text(x = 538, y = 410, labels = "-0.5", srt = -76, cex = 0.8);
text(x = 460, y = 390, labels = "-0.1", srt = 72, cex = 0.8);
text(x = 495, y = 260, labels = "0.0", srt = -12, cex = 0.8);
text(x = 720, y = 790, labels = "2.2", srt = 8, cex = 0.8);
text(x = 720, y = 630, labels = "0.9", srt = -58, cex = 0.8);
text(x = 690, y = 400, labels = "1.6", srt = 54, cex = 0.8);
text(x = 740, y = 260, labels = "0.8", srt = -8, cex = 0.8);
Loci  <- matrix(data = c(0.1, -0.1, 0.2), nrow = 1);
Hdn1  <- matrix(data = c(0.4, -1.2, 0.2, 0.1, -0.6, 2.2), nrow = 3, ncol = 2);
Hdn2  <- matrix(data = c(1.3, -0.1, -0.5, 0.0), nrow = 2, ncol = 2);
Hdn3  <- matrix(data = c(2.2, 1.6, 0.9, 0.8), nrow = 2, ncol = 2);
Tvals <- Loci %*% Hdn1 %*% Hdn2 %*% Hdn3;
text(x = Tx, y = Ty, labels = rev(Tvals), cex = 0.8);
```
